\documentclass{article}

% Set margins & headers
\usepackage[margin=1in, left=1.5in]{geometry}
  \newcommand{\bigmargins}{\vspace*{0.5in}}
\usepackage{fancyhdr}
  % Header
  \renewcommand{\headrulewidth}{0.0pt} %optional horizontal rule thickness
  \lhead{} \chead{} \rhead{\thepage} %sets header left center right
  % Footer
  \renewcommand{\footrulewidth}{0.0pt} %optional horizontal rule thickness
  \lfoot{} \cfoot{} \rfoot{} %sets footer left center right
\pagestyle{fancy}%ADD HEADER FOOTER TO PAGE EXCEPT TITLE PAGE %ensure fancyhdr is applied to doc
%USE \thispagestyle{EMPTY} BELOW MAKETITLE IF YOU USE IT OR \thispagestyle{FANCY}

% Set font (reluctantly)
\usepackage{times}

% Set spacing
\usepackage{setspace}
  \doublespace
  \renewcommand{\arraystretch}{1.3}
\usepackage{enumitem}
  \setlist{noitemsep}

% Set bibliography style
\usepackage{natbib}
\usepackage{apalike}

% Set table options
\usepackage{array}
  \newcolumntype{L}{>{\raggedright}m}

% Add other packages
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
  \graphicspath{ {images/} }
\usepackage[hidelinks]{hyperref}
  \renewcommand{\sectionautorefname}{Section}
  \renewcommand{\subsectionautorefname}{section}

% Set title
\newcommand{\mytitle}{Visualizing Women in Technology}

\begin{document}

% Abstract
%------------------------------------------------------------------------------
\thispagestyle{empty}
\singlespace
%% TODO: Verify number of pages
\noindent Katherine E. Shaw. \mytitle. A Master's Paper for the M.S. in I.S. degree. April, 2017. 26 pages. Advisor: David Gotz

\vspace{0.2in} %% TODO: correct spacing here

\noindent \textcolor{magenta}{ABSTRACT GOES HERE} %% TODO: Write abstract

\vspace{1in} %% TODO: correct spacing here

\doublespace
\noindent Headings:

Information Visualization

\textcolor{magenta}{Heading 2}

\textcolor{magenta}{Heading 3}


\clearpage
%------------------------------------------------------------------------------


% Title Page
%------------------------------------------------------------------------------
\bigmargins
\thispagestyle{empty}
\begin{center}
\MakeUppercase{\mytitle}

\vspace{1in} %% TODO: Correct Spacing Here %%
{\singlespace by\\Katherine E. Shaw

}

\vspace{1in} %% TODO: Correct Spacing Here %%
{\singlespace
  A Master's paper submitted to the faculty\\
  of the School of Information and Library Science\\
  of the University of North Carolina at Chapel Hill\\
  in partial fulfillment of the requirements\\
  for the degree of Master of Science in\\
  Information Science.

}

\vspace{1in} %% TODO: Correct Spacing Here %%
Chapel Hill, North Carolina

April 2017

\vspace{1in} %% TODO: Correct Spacing Here %%
\hfill\begin{tabular}{@{}p{3.25in}@{}}
Approved by \\

\\ \hline
David Gotz
\end{tabular}

\end{center}
\clearpage
%------------------------------------------------------------------------------

% TOC
%------------------------------------------------------------------------------
\bigmargins
\setcounter{page}{1}
\tableofcontents
\clearpage
%------------------------------------------------------------------------------


% Paper contents!
%------------------------------------------------------------------------------
\bigmargins
\section{Introduction}
Technology in modern society is ubiquitous, economically explosive, and culturally male. The stereotype of the young white male software developer is still the norm in information technology (IT) fields, even after decades of intervention to increase diversity in tech. According to the National Center for Women in Tech, in 2015 women made up 57\% of the U.S. workforce but held just 25\% of professional computing jobs; they likewise received more than half of all U.S. bachelor's degrees but only 17\% of degrees in computer science, down from 37\% in 1985 \citep{NCWIT2016Women}. Despite the large body of research documenting the underrepresentation of women in IT \textcolor{magenta}{(Citation Needed)}, technology has not seen the same progress toward gender parity observed in the other STEM fields \textcolor{magenta}{(Citation Needed)}. %% TODO: Add Citations

Researchers have proposed many explanations for the persistent gender imbalance in IT\@. Some focus on early exposure to computing, some on the importance of formal programming education, and some on hiring practices within the tech industry. The data on computer science education and technical employment support all of these interpretations, but few studies discuss more than one at a time. This project uses interactive visualization to combine these sources of data and present a holistic picture of the state of women's representation within IT\@.

\textcolor{Magenta}{EXPAND THIS} %% TODO: Expand Intro

\input{lit-review}

\input{design}

\input{development}

\input{testing}

\input{conclusion}

% Bibliography
%------------------------------------------------------------------------------
\clearpage
\bigmargins
\bibliographystyle{apalike}
\bibliography{women-in-tech.bib}
%------------------------------------------------------------------------------


\end{document}
